\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-12 tex/paper.tex
save

In this work, we repurpose adversarial training as a means to constraint the
predictive model $f$ in order to satisfy Eqn.~\ref{eqn:criterion}. In
particular, we pit $f$ against an adversary model $r := p_{\theta_r}(z |
f(X;\theta_f))$ of parameters $\theta_r$ and associated loss ${\cal
L}_r(\theta_f, \theta_r)$. This model takes  as input realizations of $f(X;
\theta_f)$, for the current value $\theta_f$ of $f$ parameters, and produces as
output a function $p_{\theta_r}(z | f(X;\theta_f))$ modeling the posterior
probability density that $z$ parameterizes the sample $X$ observed through
$f(\cdot;\theta_f)$. If $Z$ takes discrete values, then $p_{\theta_r}$ can be
represented as a probabilistic classifier $\mathbb{R} \mapsto \mathbb{R}^{|{\cal
Z|}}$ whose output $j$ (for $j=1, \dots, |{\cal Z}|$) is the estimated
probability mass $p_{\theta_r}(z_j|f(X;\theta_f))$. Similarly, if $Z$ takes
continuous values and if we assume some parameteric distribution for
$Z|f(X;\theta_f)$ (e.g., a gaussian), then $p_{\theta_r}$ can be represented as
network whose output $j$ is the estimated value of the corresponding parameter
of that distribution (e.g., its mean and variance), and such that
$p_{\theta_r}(z|f(X;\theta_f))$ can then be evaluated for any $z \in {\cal Z}$
under that distribution.  Intuitively, if $p(f(X; \theta_f)|z)$ varies with $z$,
then the corresponding correlation can be captured by $r$. By contrast, if
$p(f(X; \theta_f)|z)$ is invariant with $z$, as we require, then $r$ should
perform poorly and be close to random guessing. Training $f$ such that it
additionally minimizes the performance of $r$ therefore acts as a regularization
towards Eqn.~\ref{eqn:criterion}.

>>>>

In this work, we repurpose adversarial training as a means to constraint the
predictive model $f$ in order to satisfy Eqn.~\ref{eqn:criterion}. In
particular, we pit $f$ against an adversary model $r := p_{\theta_r}(z |
f(X;\theta_f))$ of parameters $\theta_r$ and associated loss ${\cal
L}_r(\theta_f, \theta_r)$. This model takes  as input realizations of $f(X;
\theta_f)$, for the current value $\theta_f$ of $f$ parameters, and produces as
output a function $p_{\theta_r}(z | f(X;\theta_f))$ modeling the posterior
probability density that $z$ parameterizes the sample $X$ observed through
$f(\cdot;\theta_f)$. If $Z$ takes discrete values, then $p_{\theta_r}$ can be
represented as a probabilistic classifier $\mathbb{R} \mapsto \mathbb{R}^{|{\cal
Z|}}$ whose output $j$ (for $j=1, \dots, |{\cal Z}|$) is the estimated
probability mass $p_{\theta_r}(z_j|f(X;\theta_f))$. Similarly, if $Z$ takes
continuous values and if we assume some parameteric distribution for
$Z|f(X;\theta_f)$ (e.g., a gaussian), then $p_{\theta_r}$ can be represented as
network whose output $j$ is the estimated value of the corresponding parameter
of that distribution (e.g., its mean and variance). As in
\citep{nix1994estimating}, the estimated probability density
$p_{\theta_r}(z|f(X;\theta_f))$ can then be evaluated for any $z \in {\cal Z}$
under that distribution.  Intuitively, if $p(f(X; \theta_f)|z)$ varies with $z$,
then the corresponding correlation can be captured by $r$. By contrast, if
$p(f(X; \theta_f)|z)$ is invariant with $z$, as we require, then $r$ should
perform poorly and be close to random guessing. Training $f$ such that it
additionally minimizes the performance of $r$ therefore acts as a regularization
towards Eqn.~\ref{eqn:criterion}.
